### 2022-09-17 chapters/introduction.tex
refactoring
add : missing references

\newpage
\chapter{Motivation}
\label{chapter:introduction}

Nowadays, computers are invading our daily life from work to leisure, from fancy smartphone to an embedded peacemaker that regulates the heartbeat of people.
As human beings, we are known to use tools to enhance our bodies. And thanks to computers we pushed that step even further where now we are using machines to extend our brains. Some even argue that one day they will replace us, and therefore we created our own ending. Well this is the problem for the future generations. For the moment, the main concern of humanity is to keep this planet liveable until we find another alternative.

@@

\note{add the impact of the ict ..etc}

Researchers are trying to solve this issue through different angles.
While some scientists are trying to find an alternative green source to generate energy. others focus on reducing it's%whose?
consumption. In computer science we are concerned with the ladder solution %reference.
Therefore most of the works are done on tunning the software and the hardware in order to have a more efficient way use this energy. %more efficient way of producing programs from electricity? 
%say about hardware (i.e. superconductive materials with zero resistance)
In this thesis we are trying to find a way to make the energy consumption of the computer to be as low as possible. %on the software level
%More precisely, the purpose of this thesis is to highlight (attract attention to?) the impact of programers' choices on energy comsumption of software while running the code and to advise them with the strategies to write the greenest possible code.
Our approach is to reduce the energy consumption of the software services by changing certain parameters, such as platform, programming language, and/or the design pattern.

>>>>

\newpage

\chapter{Introduction \note{missing}}

\chapter{Motivation \note{missing}}

\label{chapter:introduction}

Nowadays, computers are invading our daily lives, from work to leisure, from fancy smartphones to an embedded peacemaker that regulates the heartbeat of people.
As human beings, we are known to use tools to enhance our bodies. And thanks to computers, we pushed that step even further, to the point where now we are using machines to extend our brains. Some even argue that one day they will replace us, and therefore we have created our own ending.

Well, this is the problem for the future generations. For the moment, the main concern of humanity is to keep this planet liveable until we find another alternative.

@@

Researchers are trying to solve this issue through different angles.
While some scientists are trying to find an alternative green source to generate energy. others focus on reducing this energy consumption.
In computer science we are concerned with the ladder solution %reference.
Therefore most of the works are done on tunning the software and the hardware in order to have a more efficient way use this energy. %more efficient way of producing programs from electricity? 
%say about hardware (i.e. superconductive materials with zero resistance)
In this thesis we are trying to find a way to make the energy consumption of the computer to be as low as possible. %on the software level
%More precisely, the purpose of this thesis is to highlight (attract attention to?) the impact of programers' choices on energy comsumption of software while running the code and to advise them with the strategies to write the greenest possible code.
Our approach is to reduce the energy consumption of the software services by changing certain parameters, such as platform, programming language, and/or the design pattern.
